### 2019-03-19 README.Rmd
Header change in README
Remove "on ordinary laptop" from README
As README is built on CI sometimes, this is no longer accurate.
Add note about loading whole DB into memory
Minor README updates, cites_parties() tweaks

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dplyr)
```
# citesdb

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = " and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

```{r install_me, eval = FALSE}
source("https://install-github.me/ecohealthalliance/citesdb")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r getdata, include = FALSE}
if (!citesdb::cites_status()) citesdb::cites_db_download()
```

```{r, warning = FALSE}
library(citesdb)
library(dplyr)
start <- Sys.time()

@@

The back-end database, [MonetDB](https://monetdb.org), is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which processes over 20 million records, on an ordinary laptop:

```{r}
stop - start
```

@@

```{r}
head(cites_metadata())

head(cites_codes())
```

@@

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

### Related work

@@

```{r, results = "asis", echo = FALSE}
print(citation("citesdb"), style = "textVersion")
```

>>>>

```{r setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(dplyr)
```

# citesdb

```{r authors, echo = FALSE, results = 'asis'}

unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = " and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

```{r install_me, eval = FALSE}

source("https://install-github.me/ecohealthalliance/citesdb")
```

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

options(width=120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r getdata, include = FALSE}

if (!citesdb::cites_status()) citesdb::cites_db_download()
```

```{r, warning = FALSE}

library(citesdb)
library(dplyr)

start <- Sys.time()

@@

(_Note that running `collect()` on all of `cites_shipments()` will load a >3GB data frame into memory!_)

The back-end database, [MonetDB](https://monetdb.org), is very fast and powerful, making such
analyses quite snappy even on such large data using normal desktops and laptops. Here's the
timing of the above query, which processes over 20 million records:

```{r}

stop - start
```

@@

```{r}

head(cites_metadata())

head(cites_codes())

head(cites_parties())
```

@@

### Basic analyses

```{r warning = FALSE}

library(ggplot2)
library(cowplot)

breaks <- seq(from = 1975, to = 2020, by = 5)

plot1 <- cites_shipments() %>%
  group_by(Year) %>%
  summarize(n_records = n()) %>%
  mutate(log10_n_records = log10(n_records)) %>%
  ggplot(aes(x = Year, y = n_records)) +
  geom_point() +
  geom_line(linetype = "dashed", size = 0.2) +
  ylab("Number of Records") +
  theme_minimal() +
  scale_x_continuous(breaks = breaks)

plot2 <- cites_shipments() %>%
  group_by(Year) %>%
  summarize(n_records = n()) %>%
  mutate(log10_n_records = log10(n_records)) %>%
  ggplot(aes(x = Year, y = log10_n_records)) +
  geom_point() +
  geom_line(linetype = "dashed", size = 0.2) +
  ylab("log10(Number of Records)") +
  ylim(1.5, 6.5) +
  theme_minimal() +
  scale_x_continuous(breaks = breaks)

plot_grid(plot1, plot2, nrow = 2)
```

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

## Related work

@@

```{r, results = "asis", echo = FALSE}

print(citation("citesdb"), style = "textVersion")
```
